---
title: "Linear Regression exercise"
author: "Michael Moran"
date: "October 15, 2017"
output: html_document
---

#Set working directory

```{r}
setwd("~/Foundations of Data Science/linear_regression/linear_regression")
list.files("dataSets") 
```

# Read and examine the states data
```{r}
states.data <- readRDS("dataSets/states.rds") 
str(states.data)
```

# summary of expense and csat columns, all rows
```{r}
sts.met.en <- subset(states.data, select = c("metro", "energy"))
summary(sts.met.en)
```

# correlation between metro and energy 
```{r}
cor(sts.met.en) 
```

# scatter plot of metro vs energy
```{r}
plot(sts.met.en)
```

# Fit our regression model
```{r}
sat.mod <- lm(energy ~ metro, 
              data=states.data) 
```

# Summarize and print the results
```{r}
summary(sat.mod) 
```

#Plot the model to evaluate for deviations from assumptions
```{r}
plot(sat.mod)
```

#Select one or more additional predictors for our model

```{r}
sts.met.en.exp <- subset(states.data, select = c("metro", "energy", "expense"))
summary(sts.met.en.exp)
```

```{r}
plot(sts.met.en.exp)
```

```{r}
cor(sts.met.en.exp)
```

```{r}
sat.mod2 <- lm(energy ~ metro + expense, data = states.data)
summary(sat.mod2)
```

#Add on to the regression equation that you created in exercise 1 by generating an interaction term and testing the interaction.
```{r}
sat.mod.en.metro_by_waste <- lm(energy ~ metro * waste, data = states.data)
```


#Try adding region to the model. Are there significant differences across the four regions?
```{r}
sat.mod.en.region <- lm(energy ~ metro * waste + region, data = states.data)
anova(sat.mod.en.region)
```




